---
title: "Lab 8"
author: "Eli Schulman"
date: "11/15/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

library(tidyverse)
library(corrplot)
library(stargazer)
library(broom)
library(here)
library(modelsummary)
library(janitor)
```


```{r}
homes <- read_csv(here("data", "slo_homes.csv")) %>% 
  clean_names()
```

Make a subseet of homes_sub that only contains the following cities:
- San Luis Obispo
- AG
- Atascadero
- Santa Maria-Orcutt

```{r}
homes_sub <- homes %>% 
  filter(city %in% c("Arroyo Grande", "San Luis Obispo", "Atascadero", "Santa Maria-Orcutt"))
```

Explore data --> summar stats (home price, based on city and sale status)

If you don't want to run code, set "eval = FALSE" in the {r} part
```{r, include = FALSE, eval = FALSE}
homes_sub %>% 
  group_by(city, status) %>% 
  summarize(mean_price = mean(price, na.rm = TRUE),
            sd_price = sd(price, na.rm = TRUE))

ggplot(data = homes_sub, aes(x = price)) + 
  geom_density(aes(color = city, fill = city), alpha = .3) +
  scale_x_continuous(limits = c(0, 3e6))

```

Explore the relationship with visualizations between sqft and price
- show color based on city and shape based on status

```{r}
ggplot(homes_sub, aes(x = sq_ft, y = price)) +
  geom_point(aes(color = city, shape = status)) +
  geom_smooth(method = lm)
```


Model the relationship with home price as DV

```{r}
homes_lm1 <- lm(price ~ city + bedrooms + bathrooms + sq_ft + price_per_sq_ft + status, data = homes_sub)

# Make a subset that only has quantitative variables

homes_quant <- homes_sub %>% 
  select(price:price_per_sq_ft)

# use cor() to olook for correlation between variables 

homes_cor <- cor(homes_quant)
homes_cor # create plot of corr value
corrplot(homes_cor, method = "shade") # visualy shows the corr value 
```

Try another homes model (homes_lm2) where wi simplify to only include the following
- city
-sqft
-status

```{r}
homes_lm2 <- lm(price ~ city + sq_ft + status, homes_sub)

plot(homes_lm2)
summary(homes_lm2)
```
Ideal model has high fit (Rsq) and low complecity (AIC)

Use AIC() to find value of each model (lower AIC is better)

```{r}
round(AIC(homes_lm1),0)
round(AIC(homes_lm2),0)
```

Try to make a new dank model

```{r}
homes_lm3 <- lm(price ~ status + sq_ft + city, homes_sub)

summary(homes_lm3)
AIC(homes_lm3)

```

Use modelsummary to show outputs side by side (or you can use stargazer)
- if you use modelsumary for multiple models, then you need to feed it as a list

```{r}
modelsummary(list(homes_lm1, homes_lm2, homes_lm3))
```

Use broom::augment() to show predictions of model

```{r}
homes_predicted <- augment(homes_lm1)
```

Done with linear regression ----------

Branch

## MY UPDATE
